NumPy---Array Computation for Python

### 2020-01-03 body.tex
Remove testing section

%Moreover, with the now prevalent need for distributed computing and the
%emergence of specialized hardware such as GPUs, many new usecases have
%arisen, which NumPy was not originally designed for.
With the recent infusion of funding and the newly formalized NEP process in
place we have been able to tackle a number of important large scale changes.
We highlight two of those below, as well as changes made to our testing
infrastructure to support hardware platforms used in large scale computing.

@@

\subsection{Testing on multiple architectures}

At the time of writing the two fastest supercomputers in the
world, Summit and Sierra, both have IBM POWER9 architectures
\cite{top500nov2019}. In late 2018, Astra, the first ARM-based
supercomputer to enter the TOP500 list, went into production\cite{
astra-wiki}. Furthermore, over 100 billion ARM processors have been
produced as of 2017\cite{arm-architecture}, making it the most 
widely used instruction set architecture in the world.

Clearly there are motivations for a large scientific computing
software library to support POWER and ARM architectures. We've extended
our continuous integration (CI) testing to include \texttt{ppc64le}
(POWER8 on Travis CI) and ARMv8 (on Shippable service). We also test
with the s390x architecture (IBM Z CPUs on Travis CI) so that we
can probe the behavior of our library on a big-endian machine.
This satisfies one of the major components of
improved CI testing laid out in a version of our roadmap
\cite{numpy-roadmap}---specifically, ``CI for more exotic
platforms."

PEP 599\cite{PEP599} lays out a plan for new Python binary wheel
distribution support, \texttt{manylinux2014}, that adds
support for a number of architectures supported by the CentOS
Alternative Architecture Special Interest Group, including
ARMv8, ppc64le, as well as s390x. We are thus well-positioned
for a future where provision of binaries on these architectures
will be expected for a library at the base of the ecosystem.

>>>>

%Moreover, with the now prevalent need for distributed computing and the
%emergence of specialized hardware such as GPUs, many new usecases have
%arisen, which NumPy was not originally designed for.
With the recent infusion of funding and the newly formalized NEP process in
place we have been able to tackle a number of important large scale changes.
We highlight two of those below.

@@
